Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
minor change to changes in S1
changes in 2 and 3

The WSSSPE3 workshop included multiple mechanisms for participation and
encouraged team building around solutions. WSSSPE3 strongly encouraged participation
of early-career scientists, postdoctoral researchers, graduate students,  
early-stage researchers, and those from underrepresented groups,
with funds provided to the conference organizers by the Moore Foundation, the
National Science Foundation (NSF), and the Software Sustainability Institute (SSI) to
support the travel of potential participants who would not otherwise be able to
attend the workshop. These
funds allowed 16 additional participants.

@@

The first call for participation requested lightning talks, where each author
could make a brief statement about work that either had been done or was needed,
with the goal of contributing to the discussion of one or more working groups.
There were~24 lightning talks submitted; after a peer-review process, 16 of
those were accepted, as discussed further in Section~\ref{sec:lightning}.

@@

Returning to the topic of his talk, Turk invited the audience to picture
scientific software as a flower on a landscape under the Sun, which may
represent a number of measurable factors such as number of citations; growth of
a community; number of contributors; amount of funding; prestigious prizes
awarded; stability of the community in terms of leadership transitions; serving
community needs; not breaking test suites; and performance on new architectures.
But all these metrics are strictly speaking \emph{proxies} for the values and
the impact scientific software bears. What we can measure does not give us
direct insight---it just gives us proxies of insight.

@@

Turk said that sustaining scientific software really meant to him conducting
scientific inquiries, often by some specific software, and sustaining the people
we care about, our careers, and the future of our fields. According to Turk, we
all have an invested stake in sustaining scientific software. Hence, having
``sustained'' projects can suffocate new projects, so we need to make sure we
do not cause novel ideas and packages to suffer at the hands of the status quo.

>>>>

The WSSSPE3 workshop included multiple mechanisms for participation and
encouraged team building around solutions. WSSSPE3 strongly encouraged participation
of early-career scientists, postdoctoral researchers, graduate students,  
early-stage researchers, and those from underrepresented groups,
with funds provided to the conference organizers by the Moore Foundation, the
National Science Foundation (NSF), and the Software Sustainability Institute (SSI) to
support the travel of potential participants who would not otherwise be able to
attend the workshop. These
funds allowed 16 additional people to attend and participate.

@@

The first call for participation requested lightning talks, where each author
could make a brief statement about work that either had been done or was needed,
with the goal of contributing to the discussion of one or more working groups.
There were~24 lightning talks submitted; after a peer-review process, 16 
were accepted, as discussed further in Section~\ref{sec:lightning}.

@@

Returning to the topic of his talk, Turk invited the audience to picture
scientific software as a flower on a landscape under the Sun, which may
represent a number of measurable factors such as number of citations; growth of
a community and number of contributors; amount of funding; prestigious prizes
awarded; stability of the community in terms of leadership transitions, serving
community needs, not breaking test suites, and performance on new architectures.
But all these metrics are strictly speaking \emph{proxies} for the values and
the impact scientific software bears. What we can measure does not give us
direct insight---it just gives us proxies of insight.

@@

Turk said that sustaining scientific software really meant to him conducting
scientific inquiries, often by some specific software, and sustaining the people
we care about, our careers, and the future of our fields. According to Turk, we
all have an invested stake in sustaining scientific software. Hence, having
``sustained'' projects can suffocate new projects, so we need to make sure we
don't cause novel ideas and packages to suffer at the hands of the status quo.
